---
title: "CalMedForce Impact"
output:
  flexdashboard::flex_dashboard:
    fig_retina: 1
    css: styles.css
    logo: CalMedForce_RGB_cobrand_tagline_reverse on PHC dark blue only.png
    smart: no
runtime: shiny
---

```{r include = FALSE}

library(tidyverse)
library(tigris)
library(viridis)
library(scales)
library(shiny)
library(knitr)
library(leaflet)
library(rsconnect)
library(flexdashboard)
library(htmltools)
library(showtext)
library(plotly)

#read in scripts
source("1.Impact_summary.R", local = TRUE)
source("2.Graduates.R", local = TRUE)
source("3.All_awardees.R", local = TRUE)

```

Impact Summary
=====================================  

Columns {data-width=800}
-------------------------------------

### CalMedForce Impact Map Summary (Cohort 1 through Cohort 5)

```{r}

renderLeaflet({
  ###Create leaflet map
awardee_map$mytext <- sprintf(
"<p style='font-size: 18px; font-family: montserrat'>%s</p>",
 awardee_map$mytext) %>% 
 lapply(htmltools::HTML)

pal <- colorNumeric(palette = "viridis",  domain = awardee_map$awardAmount, na.color = "white")

leaflet(awardee_map) %>% 
  addPolygons(fillColor = pal(awardee_map$awardAmount),
              popup = awardee_map$mytext,
              popupOptions = popupOptions(maxWidth = 500),
              label = awardee_map$County,
             labelOptions = labelOptions(style = list("font-weight" = "normal", 
                                                        padding = "3px 8px",
                                                       "font-family" = "Montserrat"),
                                          textsize = "25px",
                                          direction = "auto",
                                          interactive = TRUE),
              color = "#444444",
              smoothFactor = .5,
              weight = 1,
              opacity = 1.0,
              fillOpacity = 1,
              highlightOptions = highlightOptions(weight = 5,
                                           color = "#666",
                                           fillOpacity = 0,7,
                                           bringToFront = TRUE)) %>% 
  addLegend(title = "<p style='font-family:montserrat'>Total Funds Awarded</p>", pal = pal, values = ~awardee_map$awardAmount, opacity = 0.7,
  position = "topright", na.label = "", labFormat = labelFormat(prefix = "$"))

})

```   


Columns {data-width=200}
-------------------------------------
### Programs Awarded to Date

```{r}
renderValueBox({

  
  
total.awardees <- awardees %>% filter(Grant.ID != "") 

total.awardees <- length(total.awardees$Organization)

valueBox(total.awardees,
         caption = "<b><p style='font-family:montserrat'># of Programs Awarded</p></b>",
               icon = "fa-hospital-o",
               color = "#10C637")
})


```

### Resident Positions Funded to Date

```{r}

renderValueBox({

total.resident <- awardees %>% filter(Grant.ID != "") 
total.residents <- sum(total.resident$Total.Positions.Awarded)

valueBox(total.residents,
         caption = "<b><p style='font-family:montserrat'># of Resident Positions Funded</p></b>",
               icon = "fa-user-md",
               color = "#10C637")
})

```

### Total Funds Awarded to Date

```{r}

renderValueBox({

total.awarded <- awardees %>% filter(Grant.ID != "")

total.awarded <- scales::dollar(sum(total.awarded$Amount.Awarded) + 450000 + 450000 + 150000 + 75000) 

valueBox(total.awarded,
         caption = "<b><p style='font-family:montserrat'>Total Funds Awarded</p></b>",
               icon = "fa-money",
               color = "#10C637")
})

```

### Legend

<p style="text-decoration: underline;">Abbreviations used throughout the dashboard</p>
FM = Family Medicine <br>
IM = Internal Medicine <br>
Peds = Pediatrics <br>
OBGYN = Obstetrics and Gynecology <br>
EM = Emergency Medicine <br>

Each county that is color coded means they have GME programs that have been awarded by the CalMedForce Grant. Click on a county to view the county level summary. County level summary contains the number of programs awarded by discipline, total funds awarded by discipline, and overall totals.

Graduates
=====================================  

Sidebar {.sidebar}
-------------------------------------


```{r}

p("Graduate information is based on five years of data (2016-17 through 2020-21) that is obtained through the CalMedForce grant application. The map illustrates where graduates practice after completing residency.")

```

Column {data-width=150}
-------------------------------------

### FM Graduates

```{r}
renderValueBox({

valueBox(fm_grads,
         caption = "# of Family Medicine Graduates",
               icon = "fa-user-md",
               color = "#10C637")
})

```

### IM Graduates

```{r}

renderValueBox({

valueBox(im_grads,
         caption = "<p style='font-family:montserrat'># of Internal Medicine Graduates</p>",
               icon = "fa-user-md",
               color = "#10C637")
})

```

### Ped Graduates

```{r}
renderValueBox({

valueBox(peds_grads,
         caption = "<p style='font-family:montserrat'># of Pediatric Graduates</p>",
               icon = "fa-user-md",
               color = "#10C637")
})

```

### OBGYN Graduates

```{r}
renderValueBox({

valueBox(ob_grads,
         caption = "<p style='font-family:montserrat'># of Obstetrics and Gynecology Graduates</p>",
               icon = "fa-user-md",
               color = "#10C637")
})

```

### Combined Program Graduates

```{r}
renderValueBox({

valueBox(cb_grads,
         caption = "<p style='font-family:montserrat'># of combined<br>program graduates<br>(Internal/Pediatrics)</p>",
               icon = "fa-user-md",
               color = "#10C637")
})

```

### EM Graduates

```{r}
renderValueBox({

valueBox(em_grads,
         caption = "<p style='font-family:montserrat'># of Emergency Medicine Graduates</p>",
               icon = "fa-user-md",
               color = "#10C637")
})

```

Column {data-width=800}
-------------------------------------
### Graduates

```{r}

renderLeaflet({

  grads_cali$mytext <- sprintf(
"<p style='font-size: 18px; font-family: montserrat'>%s</p>",
 grads_cali$mytext) %>% 
 lapply(htmltools::HTML)  


pal <- colorNumeric(palette = "viridis",  domain = grads_cali$n, na.color = "white")

leaflet(grads_cali) %>% 
  addPolygons(fillColor = pal(grads_cali$n),
              color = "#444444",
              smoothFactor = .5,
              popup = grads_cali$mytext,
              label = grads_cali$County,
               labelOptions = labelOptions(style = list("font-weight" = "normal", 
                                                        padding = "3px 8px",
                                                       "font-family" = "Montserrat"),
                                          textsize = "25px",
                                          direction = "auto",
                                          interactive = TRUE),
              weight = 1,
              opacity = 1.0,
              fillOpacity = 1,
              highlightOptions = highlightOptions(weight = 5,
                                           color = "#666",
                                           fillOpacity = 0,7,
                                           bringToFront = TRUE)) %>% 
              addLegend(title = "<p style='font-family:montserrat'>Total Number of Grads</p>", pal = pal, values = ~grads_cali$n, opacity = 0.7,
  position = "topright", na.label = "")

})

```   


All Awardees
=====================================  

Inputs {.sidebar}
-------------------------------------------
Total Residents by Program Type

```{r}

p("Use this to filter by Discipline for total resident positions by program type")

selectInput(inputId = "discipline",
            label = "Select Discipline",
            choices = unique(residents_pt$Discipline),
            selected = "All Disciplines")


```


Column {data-width=500}
-------------------------------------

### Total Awardees by Discipline

```{r fig.showtext=TRUE}
renderPlotly({

  
plot_ly(data = awardees_by_discipline, x = ~Discipline, y = ~Total,
        marker = list(color = "#10C637"),
        text = awardees_by_discipline$Total, textposition = "auto") %>% 
  add_bars() %>% 
  layout(yaxis = list(title = "Positions Awarded",
                      titlefont = list(family = "montserrat"),
                      tickfont = list(family = "montserrat")),
         xaxis = list(title = "Discipline",
                      titlefont = list(family = "montserrat"),
                      tickfont = list(family = "montserrat")),
         font = list(family = "montserrat"))

})

```

### Positions Awarded by Discipline

```{r fig.showtext=TRUE}
renderPlotly({

  
plot_ly(data = residents_disicipline, x = ~Discipline, y = ~Total.Residents,
        marker = list(color = "#10C637"),
        text = residents_disicipline$Total.Residents, textposition = "auto") %>% 
  add_bars() %>% 
  layout(yaxis = list(title = "Positions Awarded",
                      titlefont = list(family = "montserrat"),
                      tickfont = list(family = "montserrat")),
         xaxis = list(title = "Discipline",
                      titlefont = list(family = "montserrat"),
                      tickfont = list(family = "montserrat")),
         font = list(family = "montserrat"))

})

```

Column
------------------------------------

### Amount Awarded by Discipline

```{r fig.showtext=TRUE}
renderPlotly({

  
plot_ly(data = amount_discipline, x = ~Discipline, y = ~funds,
        marker = list(color = "#10C637"),
        text = amount_discipline$Amount, textposition = "auto") %>% 
  add_bars() %>% 
  layout(yaxis = list(title = "Amount Awarded",
                      titlefont = list(family = "montserrat"),
                      tickfont = list(family = "montserrat")),
         xaxis = list(title = "Discipline",
                      titlefont = list(family = "montserrat"),
                      tickfont = list(family = "montserrat")),
         font = list(family = "montserrat"))

})

```

### Resident Positions by Program Type

```{r fig.showtext=TRUE}

renderPlotly({
  
  pt <- residents_pt %>% 
    filter(Discipline == input$discipline)
  
  
plot_ly(data = pt, x = ~Program.Type, y = ~Total,
        marker = list(color = "#10C637"),
        text = pt$Total, textposition = "auto") %>% 
  add_bars() %>% 
  layout(yaxis = list(title = "Positions Awarded",
                      titlefont = list(family = "montserrat"),
                      tickfont = list(family = "montserrat")),
         xaxis = list(title = "Program Type",
                      titlefont = list(family = "montserrat"),
                      tickfont = list(family = "montserrat")),
         font = list(family = "montserrat"))
  
})

```

